Comparison of FDR methods on GWAS with SummarizedBenchmark

### 2017-10-19 datasets/GWAS/GWAS-SummarizedBenchmark.Rmd
Add skeleton for SummarizedBenchmark usage on GWAS

Before moving on, we'll rename the relevant columns so that they will use common terms
across the different datasets. We'll also add a 'zscore' column, and subset on a 
toy example before moving on to the full dataset.

```{r, GWAS1-reformat}
bmi <- bmi %>% 
        dplyr::rename(pval = p_value,
               SE = stderr,
               effect_size = effect,
               ind_covariate = N) %>%
        mutate(zscore = effect_size/SE)

### experimenting on a subset of the full dataset for now
bmi <- bmi[1:10000,]
```

@@

First, we'll create an object of `BenchDesign` class to hold the data.

@@

```{r, GWAS1-benchdesign}
bd <- BenchDesign(bmi)
```

>>>>

@@

First, we'll create an object of `BenchDesign` class to hold the data. Before 
doing so, we'll rename the relevant columns so that they will use common terms
across the different datasets. We'll also add a 'zscore' column.

@@

```{r, GWAS1-benchdesign}
bmi <- bmi %>% 
        dplyr::rename(pval = p_value,
               SE = stderr,
               effect_size = effect,
               ind_covariate = N) %>%
        mutate(zscore = effect_size/SE)

### experimenting on a subset of the full dataset for now
bmi <- bmi[1:10000,]

bd <- BenchDesign(bmi)
```
